%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.35in,top=0.35in,right=0.35in,bottom=0.3in]{geometry} % Document margins
\usepackage{enumitem}
\usepackage{geometry}
 \usepackage{indentfirst} 
\geometry{a4paper,left=1.0cm,right=1.0cm,top=1.0cm,bottom=0.8cm}
\name{CHUNLEI ZHANG} 
\address{(+1)864-986-5975 \quad \\ \quad chunlez@g.clemson.edu }
\vspace{-0.5cm}
\address{128 University Village Dr, Central, SC, 29630} % Your phone number and email

\begin{document}

\vspace{-0.35cm}
\begin{rSection}{Summary}
	\begin{tabular}{ @{} >{}l @{\hspace{5ex}} l }
		Objective:   & Seeking a full-time position as an applied/data/research scientist \\
		Fluent skills: & Python (NumPy, pandas, Matplotlib, scikit-learn), Spark, Matlab, R, Git, Latex, SQL \\
		Familiar skills:& Python (Keras, Tensorflow), Java 
	\end{tabular}\\
\end{rSection}
	
%--------------------------------------------------------
%	EDUCATION SECTION
%--------------------------------------------------------
\vspace{-0.35cm}
\begin{rSection}{Education}
{\bf Clemson University, South Carolina, USA} \hfill { Aug 2015 - Dec 2019} \\ 
{Ph.D. in Electrical Engineering and Minor in Mathematics} \hfill { GPA: \bf 4.0/4.0}

\vspace{-0.2cm}
{\bf Beihang University, Beijing, China} \hfill { Sep 2011 - Jul 2015} \\ 
{ Bachelor of Engineering  in Electronic and Information Engineering} \hfill { GPA: \bf 3.9/4.0; Top: 5\%}

\end{rSection}
%--------------------------------------------------------
%	Work Experience
%--------------------------------------------------------
\vspace{-0.2cm}
\begin{rSection}{Work Experience}	
Amazon, Inc. 	\hfill {Applied Scientist Intern}\\
	\begin{rSubsection}{Explore Goods Availability into Search Relevance and Ranking Model}
		{May 2019 - Aug 2019 }{}{}		
		\setlength{\parindent}{2em}
		\item Analyzed and visualized differences of customer purchase behavior and data distribution regarding availability across holiday/non-holiday and different categories
		\item Proposed two approaches to reduce unavailability rate (UR) in TopK search results which will go into production. One approach reduced around 4\% UR on average and another reduced 10\% UR during offline experiments
		\item Created a temporal feature into ranking model, resulting in a 8\% UR reduction during holiday
			\end{rSubsection}	
\end{rSection}
%--------------------------------------------------------
%	Engineering Project
%--------------------------------------------------------
\vspace{-0.2cm}
\begin{rSection}{Data Science Projects}		
	Clemson University \\
	\begin{rSubsection}{Regression Analysis of Blood Enzyme Levels and a Health Indicator}
		{Sept 2018 - Nov 2018}{}{}		
		\setlength{\parindent}{2em} \item Applied Variance Inflation Factor (VIF) to check the potential multicollinearity within 100 kinds of blood enzyme		
		\item Fitted models based on correlation, Stepwise Regression, Ridge Regression and LASSO with proper penalty parameters
		\item Conducted hypothesis test to determine the model suitability based on p-value
		\item Selected the most appropriate model based on Akaike Information Criterion (AIC) and cross validation results		
	\end{rSubsection}	
	\vspace{-0.15cm}
		\begin{rSubsection}{Regression Analysis of Local Meteorology and Air Pollution}
			{Aug 2018 - Oct 2018}{}{}		
			\setlength{\parindent}{2em} \item Fitted linear models using forward stepwise, backward stepwise, bidirectional stepwise, and Lasso regression
			\item Visualized the standardized residual plot, QQ-plot, and ACF plot of each model to check the linear regression assumptions
			\item Conducted Box-Cox Transformation to transform non-normal dependent variable into a normal shape		
		\end{rSubsection}	
\end{rSection}

%-------------------------------------------------------------------------------------
%	Research Experience
%-------------------------------------------------------------------------------------
\vspace{-0.2cm}
\begin{rSection}{Research Experience}
 Clemson University	\hfill {Research Assistant}\\	
\begin{rSubsection}{Research on Decentralized Optimization Algorithms }
{Jan 2017 - Present }{}{}

 \setlength{\parindent}{2em}
 \item Designed two novel algorithms which enabled data privacy-preservation in decentralized optimization based on Alternating Direction Method of Multipliers (ADMM) and Subgradient Method 
\item Implemented the ADMM-based algorithm on twelve Raspberry Pi boards in C++
\end{rSubsection}	
		
\vspace{-0.15cm}
\begin{rSubsection}{Research on Application of Decentralized Optimization}{ Sep 2015 - Dec 2016  }{}{}
       \item Proposed two distributed localization algorithms based on ADMM and proved the convergence rates are $O(1/k)$
		\item Compared the proposed algorithms with some existing localization algorithms via Matlab simulations, which suggested a 15\% performance improvement in localization accuracy 
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
% PUBLICATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.2cm}
\begin{rSection}{Publications}	
	[7] \textbf{C. L. Zhang}, Y. Q. Wang, Privacy-preserving Decentralized Optimization based on ADMM. \emph{IEEE Transactions on Information Forensics and Security 14.3 (2019): 565-580.}

	\vspace{-0.2cm}	
	[6]	\textbf{C. L. Zhang}, Y. Q. Wang, Distributed event localization via alternating direction method of multipliers. \emph{IEEE Transactions on Mobile Computing 17.2 (2018): 348-361.}
	
	\vspace{-0.2cm}	
	[5] \textbf{C. L. Zhang}, Y. Q. Wang, Enabling Privacy-preservation in Decentralized Optimization.  Accepted to \emph{IEEE Transactions on Control of Network Systems}
	
	\vspace{-0.2cm}		
	[4] \textbf{C. L. Zhang}, Y. Q. Wang, Sensor Network Event Localization via Non-convex Non-smooth ADMM and Augmented Lagrangian Methods. Accepted to  \emph{IEEE Transactions on Control of Network Systems.}

	\vspace{-0.2cm}		
	[3] H. Gao, \textbf{C. L. Zhang}, M. Ahmad, Y. Q. Wang. Privacy-Preserving Average Consensus on Directed Graphs Using Push-Sum.  \emph{IEEE Conference on Communications and Network Security, 2018.}

	\vspace{-0.2cm}		
	[2] T. Shang, \textbf{C. L. Zhang}, K. Li, J. W. Liu, Nonlinear quantum network coding with classical
	communication resource.  \emph{IEEE Globecom Workshops, 2015.}

	\vspace{-0.2cm}		
	[1] \textbf{C. L. Zhang}, H. Gao,  Y. Q. Wang. Enabling Privacy-preservation in ADMM based Decentralized Optimization using Function Decomposition. Submitted to \emph{IEEE Transactions on Signal Processing.}
\end{rSection}


%----------------------------------------------------------------------------------------
%	Undergraduatte AWARDS&HONORS SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.2cm}
\begin{rSection}{Awards}
\begin{tabular}{ @{} >{}l @{\hspace{38ex}} l }
Chinese Government Award for Outstanding Self Finance Students Abroad  & 2018 \\
Harris Award for the Outstanding Graduate Researcher &2018 \\
Scholarship of Excellent Academic Performance of Beihang University & 2011-2014  \\
National Endeavor Fellowship of China (10\%) & 2012-2013\\
Academic Excellence Student of Beihang University (5\%) & 2012-2013
\end{tabular}\\
\end{rSection}

\end{document}
